SecureIt: home security\\ via Android application

### 2013-01-06 relazioni/wireless/paper.tex
Added architecture section

>>>>

\section{\textbf{Architecture}}

In figure \ref{img:architecture} is presente the developed application.

\begin{figure}[!ht]
\begin{center}
\makebox[\linewidth]{\includegraphics[scale=0.45]{resources/architecture.pdf}}
\caption{High level architecture diagram}
\label{img:architecture}
\end{center}
\end{figure}

Three parts can be identified which realize the monitoring tasks of the application. Each of that parts can be diveded in components:
\begin{itemize}
	\item \texttt{Motion Detection}:
		\begin{itemize}
			\item \texttt{CameraFragment}: active view component displayed by the Android \texttt{SDK}
			\item \texttt{Preview}: links camera hardware to the Java application
			\item \texttt{MonitorAsyncTask}: processes frames in order to detect motion
			\item \texttt{LuminanceMotionDetector}, \texttt{ImageCodec} utility classes used by \texttt{MotionAsyncTask}
		\end{itemize}
	\item \texttt{Noise Detection}:
		\begin{itemize}
			\item \texttt{MicrophoneFragment}: active view component displayed by the Android \texttt{SDK}
			\item \texttt{MicVolumePicker}: passive view showing noise level
			\item \texttt{MicSamplerTask}: periodically samples audio data using \texttt{AudioCodec}
			\item \texttt{AudioCodec}: samples microphone on demand
		\end{itemize}
	\item \texttt{Motion Detection}:
		\begin{itemize}
			\item \texttt{AccelerometerFragment}: active view component displayed by the Android \texttt{SDK}
			\item \texttt{secureit.opengl}: package of view utilities to display 3D animations
		\end{itemize}
\end{itemize}

\texttt{UploadService} is activated by an alert coming from one of the framents presented before. It uses the following tasks to perform the data upload:
\begin{itemize}
	\item \texttt{ImageUploaderTask}: uploads the captured images
	\item \texttt{AudioRecorderTask}: records the audio and uploads it
	\item \texttt{PeriodicPositionUploaderTask}: periodically sends phone position to the back-end using \texttt{WIFI} or \texttt{3G} network
	\item \texttt{Bluetooth\allowbreak Periodic\allowbreak Position\allowbreak Uploader\allowbreak Task}: periodically sends phone position using opportunistic bluetooth connectivity, activated only if no \texttt{WIFI} or \texttt{3G} network is active
	\item \texttt{BluetoothServerTask}: task responding to bluetooth messages requesting delegated position upload
	\item \texttt{DelegatedPositionUploaderTask}: periodically sends delegated phone position bluetooth connectivity
\end{itemize}

Bluetooth message exchange is done using the following modules:

\begin{itemize}
	\item \texttt{ObjectBluetoothSocket}: object oriented socket for message delivery
	\item \texttt{secureit.messages}: package containing bluetooth messages
\end{itemize}
